### 2017-09-30 TF-vldb2018/sec-intro.tex

A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
A desired team has
(i) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(ii) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=1.15]{./fig/motivation-example.eps}
\end{center}
\vspace{-3ex}
\caption{Motivation example}
\label{fig-motivation-example}
\vspace{-4ex}
\end{figure}

@@

>>>>

A headhunt helps to set up a team for a software product by searching proper candidates from $G_1$ (ignore dashed edges).
A desired team has
(i) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(ii) \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

@@

\begin{figure}[tb!]
\vspace{-2ex}
\begin{center}
\includegraphics[scale=1.15]{./fig/motivation-example.eps}
\end{center}
\vspace{-3ex}
\caption{Motivation example}
\label{fig-motivation-example}
\vspace{-4ex}
\end{figure}
